Effectful Semantics for Substructural SSA

### 2023-11-16 pldi24/paper.tex
Tap

We can now give a semantics for blocks in Figure \ref{fig:ssa-block-semantics}.
Our semantics for break statements \(\lbrb{\ell}{a}\) is given by the semantics
for splitting the context into variables which pass into dominated blocks and
variables used to compute the argument, \(\dnt{\csplits{\Gamma}{\Delta}{\Xi}}\),
with the latter passed into the semantics of the argument (which is pure, and
therefore must be lifted to \(\mc{C}_0\))
\(\dnt{\hasty{\Gamma}{1}{a}{A}{\tint}}\), with the result along with the
preserved variables passed into \(\lwk{\llhyp{\ell}{\Delta}{A}}{\ms{L}}\) to
obtain the desired target. The semantics of if-statements are given by first
splitting the context via \(\dnt{\csplits{\Gamma}{\Delta}{\Xi}}\) and then
calculating the discriminant \(\dnt{\hasty{\Delta}{1}{b}{\mb{2}}{\tint}}\),
which must be pure and therefore needs to be lifted. This is then passed through
the distributor \(\delta\), with each branch passed to the semantics of its
corresponding block \(\dnt{\haslb{\Xi}{s}{\ms{L}}}\),
\(\dnt{\haslb{\Xi}{t}{\ms{L}}}\). The semantics of \rle{let-blk} and \rle{let2-blk}
are analogous to those of \rle{let} and \rle{let2} in the expression case, with the

\TODO{some text about block semantics}

>>>>

We can now give a semantics for blocks in Figure \ref{fig:ssa-block-semantics}.
Our semantics for break statements \(\lbrb{\ell}{a}\) is given by the semantics
for splitting the context into variables which pass into dominated blocks and
variables used to compute the argument, \(\dnt{\csplits{\Gamma}{\Delta}{\Xi}}\),
with the latter passed into the semantics of the argument (which is pure, and
therefore must be lifted to \(\mc{C}_0\))
\(\dnt{\hasty{\Gamma}{1}{a}{A}{\tint}}\), with the result along with the
preserved variables passed into \(\lwk{\llhyp{\ell}{\Delta}{A}}{\ms{L}}\) to
obtain the desired target. The semantics of if-statements are given by first
splitting the context via \(\dnt{\csplits{\Gamma}{\Delta}{\Xi}}\) and then
calculating the discriminant \(\dnt{\hasty{\Delta}{1}{b}{\mb{2}}{\tint}}\),
which must be pure and therefore needs to be lifted. This is then passed through
the distributor \(\delta\), with each branch passed to the semantics of its
corresponding block \(\dnt{\haslb{\Xi}{s}{\ms{L}}}\),
\(\dnt{\haslb{\Xi}{t}{\ms{L}}}\). The semantics of \rle{let-blk} and
\rle{let2-blk} are analogous to those of \rle{let} and \rle{let2} in the
expression case, except that now the bound expression \(a\) is allowed to be
impure (and therefore in particular does not need to be upgraded).

Finally, we must give semantics for \rle{where}. To do so, we begin by giving a
semantics for control-flow graphs: \todo{this}. We can now quite easily state
the semantics of \rle{where}: we simply precompose the semantics of the inner
block \(\dnt{\haslb{\Gamma}{t}{\ms{L}}}\) with the semantics of the associated
control-flow graph \(\dnt{\lhaslb{\ms{L}}{L}{\ms{K}}}\); \todo{explain}
